### 2017-11-28 paper/sections/5_file-systems.tex
paper: addresses #49
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

These similarities among effective policies for two very different domains
suggests that the heuristics and techniques in other load balancers can be used
for cache management. This generalization may reduce the work that needs to be
done for cache management as ideas may have already been explored and could
work ``out-of-the-box".

@@

>>>>

These similarities among effective policies for two very different domains
suggests that the heuristics and techniques in other load balancers can be used
for cache management. The result suggests that the concepts and problems that
architects grapple with are transcendent and the solutions they design can be
re-used in different code bases.

@@

Before we showed how policies designed for load balancing heavily influence our
cache management in a different application and storage system. But in this
section we show how an {\it unmodified} cache management policy can be used in
a load balancing strategy.  This generalization may reduce the work that needs to
be done for load balancing as ideas may have already been explored in other
domains and could work ``out-of-the-box".
